---
title: "Lab 9 Function and Iterations"
author: "Jesus Martinez"
date: "5/19/2018"
output: html_document
---
```{r}
library(tidyverse)
library(babynames)
data(babynames)    ## SSA data
data(births)
```
#Creating my first function
```{r}
most_popular_year <- function(name_arg) 
{
  babynames %>%
    filter(name == name_arg) %>%
    group_by(year) %>%
    summarize(
      name               = name[1], 
      overall_percentage = 100 * sum(0.5 * prop)
      ) %>%
    arrange(desc(overall_percentage)) %>%
    head(1) %>%
    select(name, year, overall_percentage)
}
````
#Default Arguments
```{r}
most_popular_years <- function(name_arg, num_years) 
{
  babynames %>%
    filter(name == name_arg) %>%
    group_by(year) %>%
    summarize(
      name               = name[1], 
      overall_percentage = 100 * sum(0.5 * prop)
      ) %>%
    arrange(desc(overall_percentage)) %>%
    head(n = num_years) %>%
    select(name, year, overall_percentage)
}
```
#Iterations
```{r}
my_name_list <- c("Colin", "Megan", "Bruce", "Mary", "Arlo", "Esai")
lapply(my_name_list, FUN = most_popular_year)

lapply(my_name_list, FUN = most_popular_year) %>%
  bind_rows()
````

#Excersise5-7
```{r}

top10 <- function(data) 
{
  data %>%
    group_by(name) %>%
    summarize(births = sum(n)) %>%
    arrange(desc(births)) %>%
    head(10)
}

top10(data = babynames)


top_by_decade <- babynames %>%
  mutate(decade = 10 * floor(year / 10)) %>%
  group_by(decade) %>%
  do(top10(data = .))

top_by_decade


top_by_decade[27,]
```


-------------------------------------------------------------------FOR CREDIT------------------------------------------------------
Lab 9
**Revisit previous labs and/or projects, and identify a task you did where you could have used some combination of the tools you learned in this lab. Describe it on Slack in the #lab9 channel.
In my previous group project 1, functions could have come handy:

I was exploring how earnings differed across race.My x axis was year and my Y axis was weekly earnings per house hold. I displayed five geom_lines each whiched mapped color to race. This is what I did for that projec:

```{r}
#WHAT I ORGINIALLY HAD
earnings_plot <- ggplot(earnings_data, aes(y=earnings, x= years)) + 
  geom_line(size= 0.75, aes(y=All_Race, color= All_Race)) +
  geom_line(size= 0.75, aes(y=All_Latino, color= All_Latino)) +
  geom_line(size= 0.75, aes(y=All_Black, color= All_Black)) +
  geom_line(size= 0.75, aes(y=All_White, color= White)) +
  geom_line(size= 0.75, aes(y=All_White, color= White)) +

#HOW I COULD HAVE IMPORVED MY CODE            

Plot_Fun <function(data, y_entry , x_entry, point= 1) #NAME AND CREATE FUNCTION
{
races_list <- c(Latino,Black, White, Asian) # CREAT A VECTOR  
data %>% ggplot(aes(y= y_entry, x= x_entry))+ geom_line(size= point, aes( y = lapply(race_list))) #IMPLMENT CODE
}

Plot_Fun(earnings_data, earnings, years, point = 0.75) #PLUG IN VALUES

```
